Empirical Modeling Galaxy Size Throughout the Cosmic Web

### 2017-09-19 paper/galsize_paper.tex
Updated paper with new figs

\title[The Emergent Simplicity of Galaxy Size]
{The Emergent Simplicity of Galaxy Size}

@@

%---------------------------------------------------------------------------------------------------
\begin{figure}
\centering
\includegraphics[width=8cm]{FIGS/size_clustering_ratios_stripping_model_vs_sdss.pdf}
\caption{
{\bf $\rhalf-$dependence of galaxy clustering.}
Points with error bars show new SDSS measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj,$ compared to predictions by the model tuned to the measurements shown in Fig.~\ref{fig:scatter_plot}. We define a galaxy as ``large" or ``small" according to whether it is above or below the median size for its stellar mass, so that in each panel, the SMF of the ``large" and ``small" subsamples are identical, as described in the text. The y-axis shows {\em clustering strength ratios,} so that, for example, a y-axis value of $-0.5$ corresponds to small galaxies being $50\%$ more strongly clustered than large galaxies of comparable stellar mass. Each panel shows results separately for a different volume-limited $\mstar-$threshold samples. Fiducial model predictions appear as the solid curve in each panel.
}
\label{fig:clustering_ratio_upshot}
\end{figure}
%-----------------------------------------------------------------------------------------------------

@@

%---------------------------------------------------------------------------------------------------
\begin{figure}
\centering
\includegraphics[width=8cm]{FIGS/scrambled_size_clustering_ratios.pdf}
\caption{
{\bf Origin of the $\rhalf-$dependence of clustering.}
Here we compare our fiducial model, in which satellite galaxy size is set by $\rvir$ at the time of infall, to a set of alternative models created by shuffling the sizes of various subsamples of the fiducial mock. 
}
\label{fig:shuffle}
\end{figure}
%-----------------------------------------------------------------------------------------------------

>>>>

\title[Empirical Modeling Galaxy Size]
{Empirical Modeling Galaxy Size Throughout the Cosmic Web}

@@

%---------------------------------------------------------------------------------------------------
\begin{figure}
\centering
\includegraphics[width=8cm]{FIGS/size_clustering_ratios_stripping_coevolution.pdf}
\caption{
{\bf $\rhalf-$dependence of galaxy clustering.}
Points with error bars show new SDSS measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj,$ compared to predictions by the model tuned to the measurements shown in Fig.~\ref{fig:scatter_plot}. We define a galaxy as ``large" or ``small" according to whether it is above or below the median size for its stellar mass, so that in each panel, the SMF of the ``large" and ``small" subsamples are identical, as described in the text. The y-axis shows {\em clustering strength ratios,} so that, for example, a y-axis value of $-0.5$ corresponds to small galaxies being $50\%$ more strongly clustered than large galaxies of comparable stellar mass. Each panel shows results separately for a different volume-limited $\mstar-$threshold samples. Fiducial model predictions appear as the solid curve in each panel.
}
\label{fig:clustering_ratio_upshot}
\end{figure}
%-----------------------------------------------------------------------------------------------------

@@

%---------------------------------------------------------------------------------------------------
\begin{figure}
\centering
\includegraphics[width=8cm]{FIGS/sat_vs_cen_sizes_fracdiff.pdf}
\caption{
{\bf Origin of the $\rhalf-$dependence of clustering.}
Here we compare our fiducial model, in which satellite galaxy size is set by $\rvir$ at the time of infall, to a set of alternative models created by shuffling the sizes of various subsamples of the fiducial mock. 
}
\label{fig:shuffle}
\end{figure}
%-----------------------------------------------------------------------------------------------------
